---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# r7283

<!-- badges: start -->
<!-- badges: end -->

The goal of r7283 is to provide miscellaneous tools helpful to the developer. Currently, the 'rectangulate' function provides
a minimalist dataframe from which to begin the matrix literature review. The term 'rectangulate' refers to making a rectangle, which is reminiscent of the shape of a tidy dataframe.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
# devtools::install_github("cownr10r/r7283")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r, example}
## Not run:
# library(r7283)
# bib <- "c:/path/to/file/here.bib"
# r7283::rectangulate(bib)
## End(**Not run**)
```

The following code provides a preliminary examination of the recangulated object, and conversion of the document to factors, and a look at the factors.

```{r, evaluate = FALSE}
head(processedbibliography,3)
document <- as.factor(processedbibliography$Doc.Type)
str(document)
levels(document)
```


